Proof No Diamond (3 layers)

### 2024-01-16 Paper/proof revison.tex

		\item  We use
		$\Val_{\boldsymbol{x}}(z)$ to denote the weights of node $x$ from initial configuration vector $\boldsymbol{x}$. In the context, if we do not need to consider the input $\boldsymbol{x}$, we will omit it and write as $\Val(z)$.
		We use $bias$ to denote bias.

@@

\begin{lemma}
	\label{lemma2}
	Let $L,L'$ be consecutive layers of a compensation free DNN, and $n \in L'$. 
	Then:
		$$ \max(n_s)=\sum_{m \in L}W_{m n} \max(\hat{m}_s)+bias_n \text{ and }$$
		$$\max(\hat{n}_s)=\ReLU(\sum_{m \in L}W_{m n} \max(\hat{m}_s)+bias_n)$$

@@

%	for minimal value,	
%	$ \min(n)=\sum_{m \in L}W_{m n)\min(\)+bias_n $ and
%	$ \min(\hat{n}_s)=ReLU(\sum_{m \in L}W_{m n)\min(\hat{m}s}+bias_n)$
\end{lemma}

@@

Consider any $b$ in the next layer $L_1$.
Assume first that $S(b)=+1$.
We have $\Val(b_s)= \Val(b) = \sum_{a \in L_0} W_{ab} \Val(a) + bias_b$.
If every $W_{ab} \Val(a)$ is maximized in the same time, 
then $\Val(b_s)= \Val(b)$ is also maximized.

@@

Hence $b$ reaches is maximum in configuration $\boldsymbol{x}^*$, and the value satisfies: 
$$\max(b)=\sum_{m \in L}W_{a b} \max(a_s)+bias_b$$

@@

This implies that $\ReLU(b_s)$ is maximized at $\boldsymbol{x}^*$, and its value is 
$\ReLU(\sum_{m \in L}W_{a }\max(a_s)+bias_b)$, again uniformly reached over all $b$ at configuration $\boldsymbol{x}^*$.

@@

\begin{corollary}
	\label{cor1}
	$$\max(n)=\sum_{m \in L, W_{m n}>0}W_{m n} \max(\hat{m}) + \sum_{m \in L, W_{m n}<0}W_{mn} \min(\hat{m}) + bias_n$$
	$$\min(n)=\sum_{m \in L, W_{m n}>0}W_{m n} \min(\hat{m}) + \sum_{m \in L, W_{m n}<0}W_{mn} \max(\hat{m}) + bias_n$$
\end{corollary}

@@

	The Box absraction computes its upper bound using:
	$$\bar{f}(n)= \sum_{W_{mn}>0} W_{mn} \bar{f}(\hat{m}) + \sum_{W_{mn}<0} W_{mn} \underline{f}(\hat{m}) + bias_n$$

@@

%	as bias. In the simplified $D'$, there is no compensating path because of the definition of $I$. Therefore we can apply Theorem \ref{th1} (make a more precise corollary) to get that $z(\cdot,\boldsymbol{x}^0_J)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.

@@

%	$$b= B^0 +\sum_{a_i\in I} w_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $\boldsymbol{x}^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.

@@

%For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}w_{b_ha_i}+B_h$ ($B_h$ is the bias). 

@@

	1. $\UB(b)=\max_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$.

		2. $\LB(b)=\min_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}\LB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$. 
\end{lemma}

@@

We want to show that $\mathrm{UB}(z) = \max \Val (z)$ and $\mathrm{LB}(z) = \min \Val(z)$ for the unique output nodes and we will prove this for all $c\notin B_{zero}$ . As the MILP abstraction is a sound overapproximation, 
it suffices to show that $\mathrm{UB}\leq \max \Val(c)$ and $\mathrm{LB} \geq \min \Val(c)$. We will prove this by induction on layers from the first hidden layer to the output layer. More specifically, we will prove the following lemmas:

@@

	1. for any fixed $\boldsymbol{x}^0_J$ and for $\boldsymbol{x}^*_I$, the value for $c$ in the MILP model is a fixed number, and naturally $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)=\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$. The same is true for $\boldsymbol{x}^\#_I$.

@@

	2. for any fixed $\boldsymbol{x}^0_J$, if $S(c)=1$,  $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)=\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)= \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c) = \max_{\boldsymbol{x}_I} \Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)$. The similar for $S(c)=-1$, $\langle \LB,\min\rangle$, $x^\#_I$: we can change two of them at the same time.

@@

	If $b\in B_{pure}$, the term is $W_{bc}\mathrm{AppB}(b)$ ($\mathrm{AppB}$ is the LP approximation domain of $\ReLU$) and either $b$ is a constant in the network and so is in the MILP model (trivial case), or $S(b)$ is defined.

	We know then by induction hypothesis part 1, 2 and 3,  we have the value of $b$ in the model is fixed (part 1), and it is equal to $\max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$ or $\min_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$ (by part 2, depending on $S(b)$). Since $b$ only depends on $I$, this value also equal to $\max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I)(c)$ or $\min_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I)(c)$, and therefor equal to $\UB(b)$ or $\LB(b)$. For either of them, $\mathrm{AppB}$ will be fixed value. Hence, in this case, the term $W_{bc}\mathrm{AppB}(b)$ is also a fixed number.

	Therefore, in the MILP model, $c$ is a sum of terms that are all fixed numbers. Hence $c$ is a fixed number.

	(2) If $S(c)=1$, then we have the following:	\begin{align*}
		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq constant + \sum_{b\in B_O\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)),
	\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the sign of $W_{bc}$. Now by induction hypothesis part 2, combining with $S(b)$ and both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions, we have:\begin{align*}
	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
	&constant + \sum_{b\in B_O\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
	= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c). 
	\end{align*}  This is the first equal.

	The second is simply because $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)\geq \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)\geq\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$.	The third equal is proved in last subsection, Lemma \ref{lem:reach_max_2}. $S(c)=-1$ is similar. So we have proved part 2.

>>>>

		\item  We use
		$\Val_{\boldsymbol{x}}(z)$ to denote the weights of node $x$ from initial configuration vector $\boldsymbol{x}$. In the context, if we do not need to consider the input $\boldsymbol{x}$, we will omit it and write as $\Val(z)$.
		We use $\boldsymbol{x}_J$ to denote bias.

@@

\begin{lemma}
	\label{lemma2}
	Let $L,L'$ be consecutive layers of a compensation free DNN, and $n \in L'$. 
	Then:
	$$ \max(n_s)=\sum_{m \in L}W_{m n} \max(\hat{m}_s)+\boldsymbol{b}_n \text{ and }$$
	$$\max(\hat{n}_s)=\ReLU(\sum_{m \in L}W_{m n} \max(\hat{m}_s)+\boldsymbol{b}_n)$$

@@

	%	for minimal value,	
	%	$ \min(n)=\sum_{m \in L}W_{m n)\min(\)+\boldsymbol{b}_n $ and
		%	$ \min(\hat{n}_s)=ReLU(\sum_{m \in L}W_{m n)\min(\hat{m}s}+\boldsymbol{b}_n)$
	\end{lemma}

@@

		Consider any $b$ in the next layer $L_1$.
		Assume first that $S(b)=+1$.
		We have $\Val(b_s)= \Val(b) = \sum_{a \in L_0} W_{ab} \Val(a) + \boldsymbol{b}_b$.
		If every $W_{ab} \Val(a)$ is maximized in the same time, 
		then $\Val(b_s)= \Val(b)$ is also maximized.

@@

		Hence $b$ reaches is maximum in configuration $\boldsymbol{x}^*$, and the value satisfies: 
		$$\max(b)=\sum_{m \in L}W_{a b} \max(a_s)+\boldsymbol{b}_b$$

@@

		This implies that $\ReLU(b_s)$ is maximized at $\boldsymbol{x}^*$, and its value is 
		$\ReLU(\sum_{m \in L}W_{a }\max(a_s)+\boldsymbol{b}_b)$, again uniformly reached over all $b$ at configuration $\boldsymbol{x}^*$.

@@

	\begin{corollary}
		\label{cor1}
		$$\max(n)=\sum_{m \in L, W_{m n}>0}W_{m n} \max(\hat{m}) + \sum_{m \in L, W_{m n}<0}W_{mn} \min(\hat{m}) + \boldsymbol{b}_n$$
		$$\min(n)=\sum_{m \in L, W_{m n}>0}W_{m n} \min(\hat{m}) + \sum_{m \in L, W_{m n}<0}W_{mn} \max(\hat{m}) + \boldsymbol{b}_n$$
	\end{corollary}

@@

		The Box absraction computes its upper bound using:
		$$\bar{f}(n)= \sum_{W_{mn}>0} W_{mn} \bar{f}(\hat{m}) + \sum_{W_{mn}<0} W_{mn} \underline{f}(\hat{m}) + \boldsymbol{b}_n$$

@@

		%	as \boldsymbol{b}. In the simplified $D'$, there is no compensating path because of the definition of $I$. Therefore we can apply Theorem \ref{th1} (make a more precise corollary) to get that $z(\cdot,\boldsymbol{x}^0_J)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.

@@

		%	$$b= B^0 +\sum_{a_i\in I} w_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including \boldsymbol{b} and $\boldsymbol{x}^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.

@@

		%For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}w_{b_ha_i}+B_h$ ($B_h$ is the \boldsymbol{b}). 

@@

				1. $\UB(c)=\max_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$.

				2. $\LB(c)=\min_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}\LB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$. 
			\end{lemma}

@@

			We want to show that $\mathrm{UB}(z) = \max \Val (z)$ and $\mathrm{LB}(z) = \min \Val(z)$ for the unique output nodes and we will prove this for all $c\notin B_{zero}$ . As the MILP abstraction is a sound over-approximation, 
			it suffices to show that $\mathrm{UB}\leq \max \Val(c)$ and $\mathrm{LB} \geq \min \Val(c)$. We will prove this by induction on layers from the first hidden layer to the output layer. More specifically, we will prove the following lemmas:

@@

				1. for any fixed $\boldsymbol{x}^0_J$ and for $\boldsymbol{x}^*_I$, the value for $c$ in the MILP model is a fixed number when $\boldsymbol{x}_I,\boldsymbol{x}_J=\boldsymbol{x}^*_I,\boldsymbol{x}^0_J$. Therefore naturally $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)=\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$. The same is true for $\boldsymbol{x}^\#_I$.

@@

				2. For any fixed $\boldsymbol{x}^0_J$, if $S(c)=1$,  $\max_{\boldsymbol{x}_I} \UB_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)=\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)= \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c) = \max_{\boldsymbol{x}_I} \Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(c)$. Similar results are true: the sign of $S(c)$, consider $\LB$ and $\min$, using $x_I^\#$, if we change two among them at the same time, then the conclusion still holds.

@@

				If $b\in B_{pure}$, the term is $W_{bc}\mathrm{AppB}(b)$ ($\mathrm{AppB}$ is the LP approximation domain of $\ReLU$) and either $b$ is a constant in the network and so is in the MILP model (trivial case), or $S(b)$ is defined. Consider the second case.

				We know then by induction hypothesis part 1, 2 and 3,  we have the value of $b$ in the model is fixed (part 1), and it is equal to $\max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$ or $\min_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I,\boldsymbol{x}^0_J)(c)$ (by part 2, depending on $S(b)$). Since $b$ only depends on $I$, this value also equal to $\max_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I)(c)$ or $\min_{\boldsymbol{x}_I} \Val(\boldsymbol{x}_I)(c)$, and therefore equal to $\UB(b)$ or $\LB(b)$. For either of them, $\mathrm{AppB}$ will be fixed value. Hence, in this case, the term $W_{bc}\mathrm{AppB}(b)$ is also a fixed number.

				Therefore, in the MILP model, $c$ is a sum of fixed numbers. Hence $c$ is a fixed number.

				(2) If $S(c)=1$, then we have the following:	\begin{align*}
					\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq constant + \sum_{b\in B_O\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)),
				\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the sign of $W_{bc}$. Now by induction hypothesis part 2, combining with $S(b)$ and the fact that both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions, we have:\begin{align*}
					\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
					&constant + \sum_{b\in B_O\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
					= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c). 
				\end{align*}  This is the first equal.

				The second is simply because $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)\geq \Val_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)\geq\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(c)$.	The third equal is proved in last subsection, Lemma \ref{lem:reach_max_2}. $S(c)=-1$ and/or $x^\#_I$ is similar. This is for part 2.
